An overview of the oolong package.

### 2020-06-11 overview_gh.Rmd
Minor fix of documentation. Really ready to go.
Update documentation for BTM #21 ref #19

@@

1. Chang, J., Gerrish, S., Wang, C., Boyd-Graber, J. L., & Blei, D. M. (2009). Reading tea leaves: How humans interpret topic models. In Advances in neural information processing systems (pp. 288-296).
2. Song et al. (2020) In validations we trust? The impact of imperfect human annotations as a gold standard on the quality of validation of automated content analysis. Political Communication. [link](http://www.hyunjinsong.com/supplements/PC_Song_et_al_2020.pdf)
3. Bland, J. M., & Altman, D. (1986). Statistical methods for assessing agreement between two methods of clinical measurement. The lancet, 327(8476), 307-310.
4. Chan et al. (2020) It is not listed here, because it is still under review. Do it faster! Reviewers!

>>>>

## About Biterm Topic Model

Currently, oolong cannot generate topic intrusion tests for Biterm Topic Model.

```{r btm1}
require(BTM)
oolong_test <- create_oolong(abstracts_btm)
oolong_test
```

```{r btm2}
oolong_test <- create_oolong(abstracts_btm, abstracts$text)
oolong_test
```

@@

1. Chang, J., Gerrish, S., Wang, C., Boyd-Graber, J. L., & Blei, D. M. (2009). Reading tea leaves: How humans interpret topic models. In Advances in neural information processing systems (pp. 288-296).
2. Song et al. (2020) In validations we trust? The impact of imperfect human annotations as a gold standard on the quality of validation of automated content analysis. Political Communication. [link](http://www.hyunjinsong.com/supplements/PC_Song_et_al_2020.pdf)
3. Bland, J. M., & Altman, D. (1986). Statistical methods for assessing agreement between two methods of clinical measurement. The lancet, 327(8476), 307-310.
4. Chan et al. (2020) It is not listed here, because it is still under review. Do it faster! Reviewers!
5. Nielsen, F. Å. (2011). A new ANEW: Evaluation of a word list for sentiment analysis in microblogs. arXiv preprint arXiv:1103.2903.
